More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-09-14 2016-Weak-FH-Bisim/WeakBisim.tex
a bit of informal description before meeting

\item \TODO{proposition Ludo \& Rabea: \pNet -> P,Q dans les formules pour que ce soit moins long}
\end{itemize}
Ludo:
\begin{itemize}
\item[X] reorga sec weak bisim + thm -> 10 Juil
\item  intro et orga globale du papier -> fin aout
\end{itemize}

@@

Rabea
\begin{itemize}
\item preuve transitivite -> 10 juil
\item proofs of new theorems -> fin juillet
%\item [x] uniformiser p et P pour les pnets 
%\item [x] relectures
\end{itemize}
=== en parallele

@@

Now we define
pNet nodes, as constructors for hierarchical behavioural structures.
A pNet has a set of sub-pNets that can be either pNets or pLTSs, and a
set of Holes, playing the role of process parameters.

A composite pNet consists of a set of sub-pNets exposing
a set of actions, each of them synchronising actions in each of
the sub-pNets. The synchronisation between global actions and
internal actions is given by  \emph{synchronisation vectors}: a
synchronisation vector synchronises one or several internal actions, and
exposes a single resulting global action.

We now define the structure of pNets, the following definition relies on the definition 
of holes, leaves and sorts provided below in Definition~\ref{def-sortholeleave}.

>>>>

\item \TODO{proposition Ludo \& Rabea: \pNet -> P,Q dans les formules pour que ce soit moins long}
\item related works
\end{itemize}
Ludo:
\begin{itemize}
\item[X] reorga sec weak bisim + thm -> 10 Juil
\item[X]  intro et orga globale du papier -> fin aout
\item[NEW] explication dans semantique open pnets et composition
\end{itemize}

@@

Rabea
\begin{itemize}
\item preuve transitivite -> 10 juil
\item proofs of new theorems -> fin juillet
%\item [x] uniformiser p et P pour les pnets 
%\item [x] relectures
\end{itemize}

@@

Now we define
pNet nodes as constructors for hierarchical behavioural structures.
A pNet has a set of sub-pNets that can be either pNets or pLTSs, and a
set of Holes, playing the role of process parameters. A pNet is thus a composition operator that can receive processes as parameters; it expresses how the actions of the sub-processes synchronise.

Each sub-pNets expose
a set of actions, called \emph{internal actions}. The synchronisation between global actions exposed by the pNet and
internal actions of its sub-pNets is given by  \emph{synchronisation vectors}: a
synchronisation vector synchronises one or several internal actions, and
exposes a single resulting global action.

We now define the structure of pNets, the following definition relies on the definition 
of holes, leaves and sorts formalised below in Definition~\ref{def-sortholeleave}. Informally, holes are process parameters, leavs provide the set of pLTSs at the leaves of the hierarchical structure of a pNet, and sorts give the signature of a pNete, i.e. the actions it exposes.
